%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.


\title{LING 573 Deliverable \#1 Report}
\tiny
\author{Haobo Gu \\
  \small University of Washington \\
  {\tt haobogu@uw.edu} \\\And
 Yuanhe Tian \\
 \small University of Washington \\
  {\tt yhtian@uw.edu}\\\And
 Weifeng Jin \\
 \small University of Washington \\
  {\tt wjin@uw.edu} \\\And
 Haotian Zhu \\
 \small University of Washington \\
  {\tt haz060@uw.edu}\\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document is the template we will be using for the submission of LING 573 report in Spring 2018.
\end{abstract}

\section{Introduction}

This section contains the introduction to the deliverable project.

\section{System Overview}

This section contains the system overview of the deliverable project.

\section{Approach}

This section contains the approach of the deliverable project.

\section{Results}

This section contains the results of the deliverable project.

\section{Approach}

This section contains the discussion of the deliverable project.

\section{Conclusion}

This section contains the conclusion of the deliverable project.

\begin{thebibliography}{}

\bibitem[\protect\citename{Jurafsky and Martin}2009]{Jurafsky:72}
Dan~Jurafsky and James~H. Martin.
\newblock 2009.
\newblock {\em Speech and language processing : an introduction to natural language processing, computational linguistics, and speech recognition}
\newblock Pearson Prentice-{Hall}, Upper Saddle River, NJ.

\bibitem[\protect\citename{{Manning and Schutze}}2000]{Manning:83}
{Christopher~D. Manning and Hinrich~Schutze}.
\newblock 2000.
\newblock {\em Foundations of statistical natural language processing}.
\newblock MIT Press, Cambridge, MA.

\end{thebibliography}

\end{document}
